### 2021-09-24 README.Rmd
update README instructions
update README with new workflow and figures

We can then extrapolate this data from polymod and plot a matrix, below:

```{r sydney-synth-5, cache = TRUE}
synthetic_settings_5y_sydney <- extrapolate_polymod(
  population = sydney_age_pop,
  age_breaks = c(seq(0, 85, by = 5), Inf)
)
synthetic_settings_5y_sydney
```

@@

```{r plot-matrix-differents}
plot_matrix(synthetic_settings_5y_sydney$home)
plot_matrix(synthetic_settings_5y_sydney$work)
plot_matrix(synthetic_settings_5y_sydney$school)
plot_matrix(synthetic_settings_5y_sydney$other)
plot_matrix(synthetic_settings_5y_sydney$all)
```

@@

contact_model <- fit_setting_contacts(
  contact_data_list = polymod_setting_data,
  survey_population = polymod_population
)

>>>>

First we want to fit the model to the polymod data

```{r fit-polymod}
set.seed(2021-09-24)
polymod_contact_data <- get_polymod_setting_data()
polymod_survey_data <- get_polymod_population()

setting_models <- fit_setting_contacts(
  contact_data_list = polymod_contact_data,
  population = polymod_survey_data
  )
```

Then we take this model and extrapolate to the sydney data:

```{r sydney-synth-5}
set.seed(2021-09-24)
synthetic_settings_5y_sydney <- predict_setting_contacts(
  population = sydney_age_pop,
  contact_model = setting_models,
  age_breaks = c(seq(0, 85, by = 5), Inf)
  )

synthetic_settings_5y_sydney
```

@@

```{r plot-matrix-differents}
set.seed(2021-09-24)
plot_matrix(synthetic_settings_5y_sydney$home)
plot_matrix(synthetic_settings_5y_sydney$work)
plot_matrix(synthetic_settings_5y_sydney$school)
plot_matrix(synthetic_settings_5y_sydney$other)
plot_matrix(synthetic_settings_5y_sydney$all)
```

@@

contact_model <- fit_setting_contacts(
  contact_data_list = polymod_setting_data,
  population = polymod_population
)
